---
title: "Bayesian Approach to Hurst Exponent Estimation - Dlask et. al"
author:
  - "Neil Mascarenhas"
format: revealjs
server: shiny
execute:
  echo: false
  freeze: true
fontsize: 16pt
linestretch: 1.25
---


# Introduction

---

<div style="font-size: 180%;">
<ul>
  <li>Last time we talked about simulating fBM given a Hurst exponent; today, we do the reverse: given time series data, we estimate the Hurst exponent.</li>
  <li>There are several traditional estimators for the Hurst exponent: zero-crossings, quadratic variations, rescaled range (R/S), and the Whittle estimator. Each has strengths and limitations, particularly that most provide only point estimates, without uncertainty bounds or full sampling distributions.</li>
  <li>Bayesian estimation, in contrast, produces uncertainty bounds and sampling distributions, offering richer interpretability.</li>
</ul>
</div>

---

<div style="font-size: 200%;">
  <b>1. Traditional Methods</b>  
     &nbsp;&nbsp;&nbsp;- Zero-crossings  
     &nbsp;&nbsp;&nbsp;- Quadratic variations  
     &nbsp;&nbsp;&nbsp;- Rescaled range (R/S)  
     &nbsp;&nbsp;&nbsp;- Whittle estimator  
  <br>
  <b>2. Bayesian Estimation</b>  
     &nbsp;&nbsp;&nbsp;- Zero-Crossing Probability  
     &nbsp;&nbsp;&nbsp;- Signal Segmentation  
     &nbsp;&nbsp;&nbsp;- Optimal Segmentation  
     &nbsp;&nbsp;&nbsp;- Credible Intervals  
  <br>
</div>
---

# Traditional Methods

---

## Fractional Gaussian Noise and Its Connection to fBM

- **Fractional Brownian Motion (fBM)**:  
  A continuous-time Gaussian process $B_H(t)$ with parameter $H \in (0,1)$ (the Hurst exponent), defined by:
  $$
  \mathbb{E}[B_H(t)] = 0
  $$
  $$
  \text{Cov}(B_H(t), B_H(s)) = \frac{1}{2} \left( |t|^{2H} + |s|^{2H} - |t-s|^{2H} \right)
  $$

- **Fractional Gaussian Noise (fGn)**:  
  The stationary increment process of fBM, defined as
  $$
  x_k(H) = B_H(k+1) - B_H(k)
  $$
  for $k = 1, \dots, N$.

- fGn is a zero-mean, stationary Gaussian process characterized by $H$ and is often used as a model of fractal or long-range-dependent noise in time series.

---

<div style="text-align: center; font-size: 300%;">Zero-Crossings</div>

---

## Fractional Gaussian Noise and Autocorrelation

The autocorrelation function for the fGn is
$$
\rho_k = \frac{1}{2} \left( |k+1|^{2H} - 2|k|^{2H} + |k-1|^{2H} \right)
$$

In particular:
$$
\rho \equiv \rho_1 = 2^{2H-1} - 1
$$

---



## Probability of Zero-Crossing

For two consecutive samples $(x_k, x_{k+1})$, the joint density of the bivariate normal vector with correlation $\rho$ is:
$$
f(x_k, x_{k+1}) =
\frac{1}{2\pi \sqrt{1-\rho^2}}
\exp \left(
-\frac{1}{2(1-\rho^2)}
(x_k^2 - 2\rho x_k x_{k+1} + x_{k+1}^2)
\right)
$$

The zero-crossing probability is:
$$
p^* = \Pr(x_k x_{k+1} < 0)
$$

By variable transformation and polar coordinates, one obtains:
$$
p^* = \frac{1}{\pi} \text{arccot}\left( \frac{\rho}{\sqrt{1-\rho^2}} \right )
$$

Using $\rho = 2^{2H-1}-1$, the point estimator for $H$ is:
$$
H = 1 + \log_2 \left( \cos \frac{\pi p^*}{2} \right )
$$

Empirically, $p^*$ is approximated by the relative number of zero-crossings $Z/N$.

---

# Quadratic Variations

---

## Mean Square Increment of Fractional Brownian Motion

Let $\{B_H(t)\}$ be a fractional Brownian motion with Hurst exponent $H \in (0,1)$. The covariance function is
$$
\mathbb{E}[B_H(t)B_H(s)] = \frac{1}{2}\left( |t|^{2H} + |s|^{2H} - |t-s|^{2H} \right).
$$

The mean square increment over lag $h$ is:
$$
\mathbb{E}\left[ \left(B_H(t+h) - B_H(t)\right)^2 \right]
= \mathbb{E}[B_H(t+h)^2] + \mathbb{E}[B_H(t)^2] - 2\mathbb{E}[B_H(t+h)B_H(t)].
$$

Plugging in, since $\mathbb{E}[B_H(t)^2] = |t|^{2H}$ and $\mathbb{E}[B_H(t+h)B_H(t)] = \frac{1}{2}\left( |t+h|^{2H} + |t|^{2H} - |h|^{2H} \right)$, we obtain:
$$
\begin{align*}
\mathbb{E}\left[ \left(B_H(t+h) - B_H(t)\right)^2 \right]
&= |t+h|^{2H} + |t|^{2H} - \left( |t+h|^{2H} + |t|^{2H} - |h|^{2H} \right) \\
&= |h|^{2H}
\end{align*}
$$

Thus, for all $t$,
$$
\mathbb{E}\left[ \left(B_H(t+h) - B_H(t)\right)^2 \right] = h^{2H}
$$

---

For observed time series $\{X_t\}$:

- Compute the empirical quadratic variation at lag $h$:
  $$
  V(h) = \frac{1}{N-h} \sum_{t=1}^{N-h} (X_{t+h} - X_t)^2
  $$
- For fractional Brownian motion, $\mathbb{E}[V(h)] \propto h^{2H}$.
- Estimate $H$ by linear regression of $\log V(h)$ against $\log h$:
  $$
  \log V(h) \approx c + 2H \log h
  $$
  so $H \approx \frac{1}{2} \frac{d}{d\log h}\log V(h)$.

---

# Rescaled Range (R/S) Method

---

## Scaling Properties of the Range of Cumulative Deviations

Given a time series $\{X_t\}$ of length $N$, consider its partial sums ("cumulative deviations from the mean"):

$$
Y_t = \sum_{i=1}^t (X_i - \bar{X}_n), \qquad t=1,\ldots,n
$$

where $\bar{X}_n$ is the mean of the segment of length $n$.

- The **range** $R(n)$ of these cumulative deviations is:
  $$
  R(n) = \max_{1 \leq t \leq n} Y_t - \min_{1 \leq t \leq n} Y_t
  $$
- For a self-similar process like fractional Brownian motion (fBM) with Hurst exponent $H$, $R(n)$ grows as a power law with the segment size:
  $$
  \mathbb{E}[R(n)] \propto n^H
  $$
---

To compare signals with different variances, the range is normalized by the standard deviation $S(n)$:
  $$
  Q(n) = \frac{R(n)}{S(n)}
  $$
  where
  $$
  S(n) = \left( \frac{1}{n} \sum_{t=1}^n (X_t - \bar{X}_n)^2 \right)^{1/2}
  $$

For self-similar processes,
$$
\mathbb{E}[Q(n)] \propto n^H
$$
Therefore, if you plot $\log Q(n)$ against $\log n$, the slope gives an estimate of the Hurst exponent $H$.

---

This estimator was introduced by Hurst:  


Given a time series $\{X_t\}$ of length $N$:

- For subintervals of length $n$:
  1. Compute mean: $\bar{X}_n = \frac{1}{n} \sum_{t=1}^{n} X_t$.
  2. Form cumulative deviations: $Y_t = \sum_{i=1}^t (X_i - \bar{X}_n)$.
  3. Compute the range: $R(n) = \max_{1 \leq t \leq n} Y_t - \min_{1 \leq t \leq n} Y_t$.
  4. Compute the standard deviation: $S(n) = \left( \frac{1}{n} \sum_{t=1}^n (X_t - \bar{X}_n)^2 \right)^{1/2}$.
  5. Compute the rescaled range: $Q(n) = R(n)/S(n)$.
- For self-similar processes, $\mathbb{E}[Q(n)] \propto n^H$.
- Estimate $H$ by linear regression of $\log Q(n)$ vs. $\log n$:
  $$
  \log Q(n) \approx c + H \log n
  $$

---

# Whittle Estimator

---

- **Spectral Density:** The spectral density $f_H(\lambda)$ of fractional Gaussian noise (fGn) — and more generally of stationary long-memory processes — behaves, for small frequencies $\lambda$, as:
  $$
  f_H(\lambda) \propto |\lambda|^{-(2H-1)}
  $$
- **Periodogram as Approximate Sufficient Statistic:** For large sample size $N$, the periodogram ordinates $I(\lambda_j)$ at Fourier frequencies $\lambda_j$ are (approximately) independent and follow an exponential distribution with mean $f_H(\lambda_j)$.
- **Whittle Likelihood:** Using the (approximate) independence and exponential distribution of $I(\lambda_j)$, we can write an approximate likelihood for $H$ (and variance), allowing efficient inference even in long-memory models.

---

## Derivation of the Spectral Density for fGn

The autocovariance function of fGn is
$$
\gamma(k) = \frac{1}{2} \left(|k+1|^{2H} - 2|k|^{2H} + |k-1|^{2H}\right)
$$

The spectral density is the Fourier transform of the autocovariance:
$$
f_H(\lambda) = \sum_{k=-\infty}^{\infty} \gamma(k) e^{-i k \lambda}
$$
For small $|\lambda|$, the sum can be approximated and yields:
$$
f_H(\lambda) \propto |\lambda|^{-(2H-1)}, \quad \lambda \to 0
$$

This power-law behavior at low frequencies reflects the long-range dependence when $H > 0.5$.

---

## Why Are Periodogram Ordinates Approximately Independent and Exponentially Distributed?

Let $\{X_t\}$ be a zero-mean stationary Gaussian time series of length $N$. The (normalized) discrete Fourier transform (DFT) is
$$
\tilde{X}(\lambda_j) = \frac{1}{\sqrt{N}} \sum_{t=1}^N X_t e^{-i \lambda_j t}, \quad \lambda_j = \frac{2\pi j}{N}, \quad j=1,\dots, \Big\lfloor \frac{N}{2} \Big\rfloor
$$
The periodogram at frequency $\lambda_j$ is $I(\lambda_j) = |\tilde{X}(\lambda_j)|^2$

- For large $N$, by the central limit theorem and properties of the Fourier basis, $\tilde{X}(\lambda_j)$ becomes (approximately) a complex normal random variable, with
  $$
  \mathbb{E}\left[\,|\tilde{X}(\lambda_j)|^2\,\right] = f_H(\lambda_j)
  $$
- If $\tilde{X}(\lambda_j) \sim \mathcal{CN}(0, f_H(\lambda_j))$ (complex normal with mean zero, variance $f_H(\lambda_j)$), then $I(\lambda_j)$ (the squared modulus) is exponentially distributed:
  $$
  I(\lambda_j) \sim \text{Exp}\Big(\frac{1}{f_H(\lambda_j)}\Big)
  $$
  with mean $f_H(\lambda_j)$.
- For large $N$, DFT coefficients at different $\lambda_j$ are nearly uncorrelated (orthogonality of the basis), so $I(\lambda_j)$ are approximately independent.


---  

The Whittle estimator is a semi-parametric maximum likelihood approach leveraging the spectral density of the process.

- The spectrum at frequency $f$ behaves as $S(f) \propto |f|^{-(2H-1)}$ at low frequencies.
- The Whittle likelihood is
  $$
  L(H, \sigma^2) = \prod_{j=1}^N \frac{1}{f_H(\lambda_j)} \exp\left(-\frac{I(\lambda_j)}{f_H(\lambda_j)}\right)
  $$
  where $I(\lambda_j)$ is the periodogram at frequency $\lambda_j$ and $f_H$ is the theoretical spectral density for given $H$.
- The estimator $\hat{H}_{\text{Whittle}}$ is the value of $H$ which maximizes the (approximate) log-likelihood:
  $$
  \hat{H}_{\text{Whittle}} = \arg\max_H \log L(H, \sigma^2)
  $$
- Often restricted to low-frequency bands for better consistency.

---

# Bayesian Estimation

---

## Prior for Zero-Crossing Probability

- In the Bayesian approach, we treat the zero-crossing probability $p^*$ as a random variable.
- **Prior for $p^*$:**  
  We impose a Beta-type prior:
  $$
  f_{\text{PRIOR}}(p^*) =
  \frac{(p^*)^{-a}(1-p^*)^{-a}}{B(1-a, 1-a)}, \quad a \in [0,1)
  $$
  - $a = 0$: uniform prior (all $p^*$ equally likely).
  - $a = 1/2$: Jeffreys–Perks prior (reference prior for binomial).
- The choice of $a$ controls the informativeness of the prior.

---

## Likelihood for Zero-Crossing Counts

- Given a signal of length $N+1$ and an observed number of zero-crossings $Z$,
  the likelihood for $p^*$ is binomial:
  $$
  Z \mid p^* \sim \mathrm{Binomial}(N, p^*)
  $$
  $$
  f(Z \mid p^*) = \binom{N}{Z} (p^*)^Z (1-p^*)^{N-Z}
  $$
- Each crossing is considered a Bernoulli trial, with probability $p^*$ that the sign changes between consecutive values.

---

## Posterior for Zero-Crossing Probability

- **Posterior (using Bayes' theorem):**
  $$
  f_{\text{POST}}(p^* \mid Z) =
  \frac{
  (p^*)^{Z-a} (1-p^*)^{N-Z-a}
  }{
  B(Z+1-a,\ N-Z+1-a)
  }
  $$
- In other words, the posterior is a Beta distribution:
  $$
  p^* \mid Z \sim \mathrm{Beta}(Z+1-a,\, N-Z+1-a)
  $$
- This posterior for $p^*$ is then mapped to a posterior for the Hurst exponent $H$ via the transformation:
  $$
  H \approx 1 + \log_2\left( \cos \frac{\pi p^*}{2} \right)
  $$

---

# Signal Segmentation

---

## Why Segment the Signal?

<div style="font-size: 150%;">

* Real-world signals (EEG, finance, environmental data) often exhibit **time-varying roughness** and are not globally well-modeled by a single Hurst exponent.
* Fractional Gaussian noise (fGn) is *stationary* only in the increments; empirical data may be only **locally stationary**.
* To detect structural changes in persistence or anti-persistence, we divide the observed signal into **non-overlapping segments**, estimate local $H$ in each, and analyze its behavior over time.

</div>

---

## Segmentation Framework

* Take a time series of length $L(N+1)$.
* Partition it into $L$ disjoint segments, each containing $N+1$ points:
  $$
  \{x_1,\dots,x_{N+1}\},\quad \{x_{N+2},\dots,x_{2N+2}\},\dots
  $$
* Let $Z_k$ denote the number of zero-crossings in segment $k$,
  $k = 1,\dots,L$.

Because each segment is modeled as fGn with its own zero-crossing count, each segment contributes a **segment-wise posterior** for the zero-crossing probability $p$:
$$
p \mid Z_k \sim \mathrm{Beta}(Z_k+1-a,\, N-Z_k+1-a).
$$

---

## The Aggregate Posterior for $p$

For the entire segmented signal, define the **aggregate probability density**:
$$
f_L(p) =
\frac{1}{L}\sum_{k=1}^{L}
\frac{
p^{Z_k - a}\,(1-p)^{N - Z_k - a}
}{
B(Z_k+1-a,\, N-Z_k+1-a)
}.
$$

Interpretation:

* Each segment contributes a Beta-shaped posterior based on its own zero-crossing count.
* $f_L(p)$ is simply the **mixture** of segment posteriors.
* When the signal has homogeneous roughness, these posteriors overlap and $f_L(p)$ is sharply peaked.
* When roughness varies, segment posteriors differ, and $f_L(p)$ broadens or becomes multimodal.

---

## From Aggregate Posterior to Posterior of $H$

Since
$$
H = 1 + \log_2\left( \cos\frac{\pi p}{2} \right),
$$
and this mapping is monotone, the distribution of $H$ follows immediately from $f_L(p)$.

Mean:
$$
E(H) = 1 + \int_0^1 f_L(p)\,\log_2\left(\cos\frac{\pi p}{2}\right)\,dp.
$$

Variance:
$$
\sigma^2(H) =
\int_0^1
\left[1+\log_2\left(\cos\frac{\pi p}{2}\right)\right]^2 f_L(p)\,dp
- [E(H)]^2.
$$

These quantities summarize the **overall roughness and variability** across all segments.

---

# Optimal Segmentation

---

## Why Choose $L$ Carefully?

<div style="font-size: 150%;">

* If $L$ is too small (segments too long):
  local structure is averaged out → **missed regime changes**.
* If $L$ is too large (segments too short):
  zero-crossing counts become noisy → posteriors broaden and become unstable.
* We need a principled rule to select the **optimal number of segments** $L^*$.

</div>

---

## Axiom 1: Unimodality of $f_L(p)$

The aggregate posterior $f_L(p)$ should be **unimodal**.

Rationale:

* If the underlying process has approximately constant roughness within each segment,
  the individual segment posteriors should align in a common region.
* Their mixture should then have **a single dominant peak**.
* Multimodality typically signals:

  * insufficient data per segment,
  * excessive segmentation,
  * or large, unmodeled heterogeneity.

Thus **unimodality ensures statistical coherence** of the segmentation.

---

## Axiom 2: Minimum Sufficient Segmentation

Among all $L$ for which $f_L(p)$ is unimodal, choose the **smallest** such $L > 1$:

$$
L^* =
\begin{cases}
1, & \text{if $f_L(p)$ is unimodal for all tested segmentations} \\
\min_{L>1}\{L : f_L(p)\ \text{is unimodal}\}, & \text{otherwise}
\end{cases}
$$

Interpretation:

* We want **the simplest segmentation** that yields a stable, unimodal posterior.
* In practice, this coincides with minimizing the **posterior variance** of $H$.

---

## Credible Interval Construction Under $L^*$

Given the optimal segmentation $L^*$, compute boundaries $p_{\min}, p_{\max}$ from:
$$
\int_0^{p_{\min}} f_{L^*}(p)\,dp = \frac{\alpha}{2}, \qquad
\int_0^{p_{\max}} f_{L^*}(p)\,dp = 1 - \frac{\alpha}{2}.
$$

Transform via the monotone mapping to obtain a credible interval for $H$:
$$
H_{\min} = 1 + \log_2\left(\cos\frac{\pi p_{\max}}{2}\right), \qquad
H_{\max} = 1 + \log_2\left(\cos\frac{\pi p_{\min}}{2}\right).
$$

These are fully Bayesian uncertainty bounds capturing segmentation variability, binomial uncertainty, and transformation uncertainty.

---

## References

**Primary Source:**
- Dlask, M., & Kukal, J. (2017). Bayesian Approach to Hurst Exponent Estimation. *Methodology and Computing in Applied Probability*, 19(3), 1-15. doi:10.1007/s11009-017-9543-x[1][2]

**Fractional Brownian Motion and fGn:**
- Mandelbrot, B. B., & Van Ness, J. W. (1968). Fractional Brownian Motions, Fractional Noises and Applications. *SIAM Review*, 10(4), 422-437. doi:10.1137/1010093[3][4][5]
- Kolmogorov, A. N. (1940). Wienersche Spiralen und einige andere interessante Kurven im Hilbertschen Raum. *Doklady Academy of Sciences USSR*, 26, 115-118[6]

**Traditional Hurst Exponent Estimators:**
- Hurst, H. E. (1951). Long-term storage capacity of reservoirs. *Transactions of the American Society of Civil Engineers*, 116, 770-799[7][8][9]
- Whittle, P. (1953). Estimation and information in stationary time series. *Arkiv för Matematik*, 2, 423-434[10][11][12]
- Beran, J. (1994). *Statistics for Long-Memory Processes*. Chapman and Hall, New York[13][14][15]

**Bayesian Hurst Estimation:**
- Tyralis, H., & Koutsoyiannis, D. (2011). Simultaneous estimation of the parameters of the Hurst-Kolmogorov stochastic process. *Stochastic Environmental Research & Risk Assessment*, 25(1), 21-33. doi:10.1007/s00477-010-0408-x[16][17][18]
- Tyralis, H., & Koutsoyiannis, D. (2014). A Bayesian statistical model for deriving the predictive distribution of hydroclimatic variables. *Climate Dynamics*, 42, 2867-2883[19]

**Bayesian Statistical Methods:**
- Jeffreys, H. (1939). *Theory of Probability*. Oxford University Press[20][21][22]
- Jeffreys, H. (1961). *Theory of Probability* (3rd ed.). Oxford University Press[23]

**Spectral Analysis and Locally Stationary Processes:**
- Dahlhaus, R. (1996). On the Kullback-Leibler information divergence of locally stationary processes. *Stochastic Processes and their Applications*, 62(1), 139-168. doi:10.1016/0304-4149(95)00090-9[24][25]
- Dahlhaus, R. (2012). Locally Stationary Processes. In T. S. Ferguson et al. (Eds.), *Handbook of Statistics*, Vol. 30 (pp. 351-413). Elsevier[26][27]

---


```{r}
#| context: setup

library(magick)

# ===================================================================
# fBM SIMULATION METHODS IMPLEMENTATION
# ===================================================================
# This section implements all 6 methods for simulating Fractional Brownian Motion:
# 
# 1. HOSKING ALGORITHM: Sequential conditioning on past values
#    - Time: O(N²), Space: O(N²)
#    - Best for: Small samples (N < 5,000)
#    - Exact method capturing full covariance
#
# 2. CHOLESKY DECOMPOSITION: Direct matrix factorization
#    - Time: O(N³), Space: O(N²)
#    - Best for: Small samples (N < 1,000)
#    - Simplest and most intuitive exact method
#
# 3. FFT (CIRCULANT EMBEDDING): Circulant matrix via FFT
#    - Time: O(N log N), Space: O(N)
#    - Best for: Large samples (N > 5,000)
#    - Industry standard; near-exact with boundary corrections
#
# 4. CORRELATED RANDOM WALK: Aggregation-based approximation
#    - Time: O(N^{2-2H}), Space: O(N)
#    - Best for: Theory, error control, streaming
#    - Approximates covariance asymptotically
#
# 5. RANDOM MIDPOINT DISPLACEMENT: Bisection with local conditioning
#    - Time: O(N), Space: O(1) worst-case
#    - Best for: Streaming/unknown horizon
#    - Exact conditioning on local neighborhood
#
# 6. SPECTRAL METHOD: Frequency-domain approximation via FFT
#    - Time: O(N log N), Space: O(N)
#    - Best for: Very large N, speed critical
#    - ~4x faster than FFT with Paxson's spectral density approx
# ===================================================================


generate_fbm_hosking <- function(n, H) {
  # Compute autocovariance
  gamma <- function(k) {
    if (k == 0) return(1)
    0.5 * (abs(k + 1)^(2*H) - 2*abs(k)^(2*H) + abs(k - 1)^(2*H))
  }
  
  Z <- numeric(n)
  Z[1] <- rnorm(1)
  
  if (n == 1) return(cumsum(Z))
  
  # Build covariance matrix incrementally
  cov_matrix <- matrix(0, n, n)
  cov_matrix[1, 1] <- 1
  
  for (i in 1:(n-1)) {
    # Build i x i covariance matrix
    for (j in 1:i) {
      for (k in 1:i) {
        cov_matrix[j, k] <- gamma(abs(j - k))
      }
    }
    
    # Conditional mean and variance
    c_vec <- sapply(1:i, function(k) gamma(k + 1))
    
    cov_inv <- tryCatch(
      solve(cov_matrix[1:i, 1:i]),
      error = function(e) solve(cov_matrix[1:i, 1:i] + diag(1e-8, i))
    )
    
    mu <- as.numeric(crossprod(c_vec, cov_inv %*% Z[1:i]))
    sigma2 <- 1 - as.numeric(crossprod(c_vec, cov_inv %*% c_vec))
    sigma2 <- max(sigma2, 1e-8)
    
    Z[i + 1] <- mu + sqrt(sigma2) * rnorm(1)
  }
  
  cumsum(Z)
}

# ===================================================================
# METHOD 2: CHOLESKY DECOMPOSITION
# ===================================================================
generate_fbm_cholesky <- function(n, H) {
  # Create covariance matrix
  cov_matrix <- matrix(0, n, n)
  for (i in 1:n) {
    for (j in 1:n) {
      cov_matrix[i, j] <- 0.5 * (abs(i - j + 1)^(2*H) - 
                                  2*abs(i - j)^(2*H) + 
                                  abs(i - j - 1)^(2*H))
    }
  }
  
  # Cholesky decomposition
  L <- tryCatch(
    chol(cov_matrix),
    error = function(e) {
      chol(cov_matrix + diag(1e-6, n))
    }
  )
  
  # Generate standard normal increments
  Z <- rnorm(n)
  
  # Generate FBM
  fbm <- crossprod(L, Z)
  cumsum(as.vector(fbm))
}

# ===================================================================
# METHOD 3: FFT (CIRCULANT EMBEDDING METHOD)
# ===================================================================
generate_fbm_fft <- function(n, H) {
  gamma <- function(k) {
    if (k == 0) return(1)
    0.5 * (abs(k + 1)^(2*H) - 2*abs(k)^(2*H) + abs(k - 1)^(2*H))
  }
  
  # Extend to power of 2
  M <- 2^ceiling(log2(2*n))
  
  # Build circulant covariance
  circ_cov <- c(sapply(0:(n-1), gamma), rep(0, M - n))
  circ_cov[(M-n+1):M] <- sapply((n-1):1, gamma)
  
  # FFT of first row
  lambda <- Re(fft(circ_cov))
  
  # Ensure positive (adjust if needed)
  if (any(lambda < -1e-10)) {
    M <- 2 * M
    circ_cov <- c(sapply(0:(n-1), gamma), rep(0, M - n))
    circ_cov[(M-n+1):M] <- sapply((n-1):1, gamma)
    lambda <- Re(fft(circ_cov))
  }
  
  # Take square root
  sqrt_lambda <- sqrt(pmax(lambda, 0))
  
  # Generate samples
  U <- rnorm(M)
  U_fft <- fft(U)
  Z_fft <- sqrt_lambda * U_fft
  Z <- Re(fft(Z_fft, inverse = TRUE)) / M
  
  cumsum(Z[1:n])
}

# ===================================================================
# METHOD 4: CORRELATED RANDOM WALK (Approximate)
# ===================================================================
generate_fbm_crw <- function(n, H, M = NULL) {
  if (is.null(M)) {
    # Heuristic for aggregation level
    M <- max(2, floor(sqrt(n / (1 - H))))
  }
  
  # Generate M correlated sequences
  X <- matrix(0, n, M)
  
  for (j in 1:M) {
    # Generate uniform random variables
    U <- runif(n)
    
    # Transform to get correlated increments
    mu_vec <- (1 - U)^(1 / (2 - 2*H))
    
    # Apply sign randomness
    signs <- sample(c(-1, 1), n, replace = TRUE)
    X[, j] <- cumsum(signs * mu_vec)
  }
  
  # Average and scale
  c_H <- sqrt(pi * H / sin(pi * H)) * 2^H
  fbm_approx <- c_H * rowMeans(X)
  
  fbm_approx
}

# ===================================================================
# METHOD 5: RANDOM MIDPOINT DISPLACEMENT (RMD)
# ===================================================================
generate_fbm_rmd <- function(n, H, m = 10, n_neighbors = 10) {
  gamma <- function(k) {
    if (k == 0) return(1)
    0.5 * (abs(k + 1)^(2*H) - 2*abs(k)^(2*H) + abs(k - 1)^(2*H))
  }
  
  # Bisection-based approach
  result <- numeric(n)
  result[1] <- 0
  
  if (n == 1) return(result)
  
  result[n] <- rnorm(1)
  
  # Recursive bisection
  bisect_fill <- function(left, right, result) {
    if (right - left < 2) return(result)
    
    mid <- (left + right) %/% 2
    
    # Determine neighbors
    n_left <- min(n_neighbors, mid - left)
    n_right <- min(n_neighbors, right - mid)
    
    left_idx <- max(left, mid - n_left)
    right_idx <- min(right, mid + n_right)
    
    neighbor_idx <- c(left_idx:(mid-1), (mid+1):right_idx)
    neighbor_vals <- result[neighbor_idx]
    
    if (length(neighbor_idx) > 0) {
      neighbor_distances <- abs(neighbor_idx - mid)
      
      # Build covariance
      cov_mat <- matrix(0, length(neighbor_idx) + 1, length(neighbor_idx) + 1)
      for (i in 1:(length(neighbor_idx)+1)) {
        for (j in 1:(length(neighbor_idx)+1)) {
          if (i == length(neighbor_idx) + 1 & j == length(neighbor_idx) + 1) {
            cov_mat[i, j] <- 1
          } else if (i == length(neighbor_idx) + 1 | j == length(neighbor_idx) + 1) {
            idx <- if (i == length(neighbor_idx) + 1) j else i
            cov_mat[i, j] <- gamma(abs(neighbor_idx[idx] - mid))
          } else {
            cov_mat[i, j] <- gamma(abs(neighbor_idx[i] - neighbor_idx[j]))
          }
        }
      }
      
      # Condition on neighbors
      cov_inv <- tryCatch(
        solve(cov_mat[-nrow(cov_mat), -ncol(cov_mat)]),
        error = function(e) diag(1e-8, nrow(cov_mat) - 1)
      )
      
      mu <- as.numeric(cov_mat[nrow(cov_mat), -ncol(cov_mat)] %*% cov_inv %*% neighbor_vals)
      sigma2 <- 1 - as.numeric(cov_mat[nrow(cov_mat), -ncol(cov_mat)] %*% cov_inv %*% 
                               cov_mat[-nrow(cov_mat), ncol(cov_mat)])
      sigma2 <- max(sigma2, 1e-8)
      
      result[mid] <- mu + sqrt(sigma2) * rnorm(1)
    } else {
      result[mid] <- rnorm(1)
    }
    
    result <- bisect_fill(left, mid, result)
    result <- bisect_fill(mid, right, result)
    result
  }
  
  result <- bisect_fill(1, n, result)
  cumsum(result)
}

# ===================================================================
# METHOD 6: SPECTRAL METHOD (Fast FFT approximation)
# ===================================================================
generate_fbm_spectral <- function(n, H) {
  # Extended to power of 2
  N <- 2^ceiling(log2(n))
  
  # Spectral density approximation for fGn
  spectral_density <- function(lambda, H) {
    if (lambda == 0) return(1)
    # Paxson's approximation
    term1 <- 2 * sin(pi * H) * gamma(2*H + 1) * (1 - cos(lambda)) * abs(lambda)^(-2*H - 1)
    term2 <- abs(lambda)^(1 - 2*H) * (1 - cos(lambda))
    max(term1 + term2, 0)
  }
  
  # Compute spectral density at Fourier frequencies
  freqs <- 2 * pi * (0:(N-1)) / N
  spec <- sapply(freqs, function(f) spectral_density(f, H))
  spec <- pmax(spec, 0)
  
  # Generate coefficients
  a <- complex(N)
  for (k in 1:(N-1)) {
    a[k] <- sqrt(spec[k] / N) * (rnorm(1) + 1i * rnorm(1)) / sqrt(2)
  }
  a[1] <- sqrt(spec[1] / N) * rnorm(1)
  
  # Enforce symmetry for real output
  for (k in 2:(N/2)) {
    a[N - k + 2] <- Conj(a[k])
  }
  
  # Inverse FFT
  Z <- Re(fft(a, inverse = TRUE)) / sqrt(N/2)
  
  cumsum(Z[1:n])
}

# Wrapper function to select method
generate_fbm <- function(n, H, method = "cholesky") {
  method <- tolower(method)
  
  switch(method,
    "hosking" = generate_fbm_hosking(n, H),
    "cholesky" = generate_fbm_cholesky(n, H),
    "fft" = generate_fbm_fft(n, H),
    "crw" = generate_fbm_crw(n, H),
    "rmd" = generate_fbm_rmd(n, H),
    "spectral" = generate_fbm_spectral(n, H),
    generate_fbm_cholesky(n, H)  # Default to Cholesky
  )
}

# Helper to compute frame indices used by both animations
calc_frame_indices <- function(n_steps) {
  frame_skip <- max(1, floor(n_steps / 100))
  sort(unique(c(seq(1, n_steps, by = frame_skip), n_steps)))
}

# Function to create animation frames
create_animation_frames <- function(path, H, n_steps, method = "cholesky", frame_indices = NULL) {
  frames <- list()
  
  if (is.null(frame_indices)) {
    frame_indices <- calc_frame_indices(n_steps)
  } else {
    frame_indices <- sort(unique(frame_indices))
  }
  
  for (step in frame_indices) {
    temp_file <- tempfile(fileext = ".png")
    
    png(temp_file, width = 700, height = 500, res = 100)
    
    plot(
      1:n_steps,
      path,
      type = "n",
      lwd = 2.5,
      col = "#2E86AB",
      xlab = "Time",
      ylab = "Position",
      main = paste0("fBM Simulation: H = ", round(H, 2), 
                    " | ", method, " | Step: ", step, "/", n_steps),
      cex.main = 1.5,
      cex.lab = 1.2
    )
    
    grid(nx = 20, ny = 20, col = "lightgray", lty = 2)
    
    if (step > 0) {
      lines(1:step, path[1:step], lwd = 2.5, col = "#2E86AB")
      points(step, path[step], col = "#E74C3C", cex = 1.5, pch = 16)
    }
    
    if (H > 0.55) {
      interpretation <- "Persistent (Trending)"
      text_col <- "#A23B72"
    } else if (H < 0.45) {
      interpretation <- "Mean-Reverting"
      text_col <- "#F18F01"
    } else {
      interpretation <- "Standard BM"
      text_col <- "#C73E1D"
    }
    
    mtext(interpretation, side = 3, line = -1.5, col = text_col, font = 2, cex = 1.2)
    
    dev.off()
    frames[[length(frames) + 1]] <- image_read(temp_file)
    unlink(temp_file)
  }
  
  animation <- do.call(c, frames)
  animation <- image_animate(animation, fps = 10, loop = 1)
  
  return(animation)
}

estimate_zero_crossings <- function(path) {
  dx <- diff(path)
  if (length(dx) < 2) return(NA_real_)
  dx <- dx - mean(dx)
  signed <- sign(dx)
  signed[signed == 0] <- NA
  crossings <- sum(signed[-1] * signed[-length(signed)] < 0, na.rm = TRUE)
  denom <- max(1, length(dx) - 1)
  p_star <- crossings / denom
  p_star <- pmin(pmax(p_star, 1e-6), 1 - 1e-6)
  1 + log2(cos(pi * p_star / 2))
}

estimate_quadratic_variation <- function(path, max_lag = 10) {
  n <- length(path)
  if (n < 5) return(NA_real_)
  max_h <- min(max_lag, floor((n - 1) / 2))
  if (max_h < 2) return(NA_real_)
  h_vals <- seq_len(max_h)
  V <- sapply(h_vals, function(h) {
    diffs <- path[(h + 1):n] - path[1:(n - h)]
    mean(diffs^2)
  })
  positive_v <- V > 0
  if (!any(positive_v)) return(NA_real_)
  fit <- lm(log(V[positive_v]) ~ log(h_vals[positive_v]))
  slope <- coef(fit)[2]
  as.numeric(slope / 2)
}

estimate_rs <- function(path) {
  n <- length(path)
  if (n < 2) return(NA_real_)
  mean_val <- mean(path)
  Y <- cumsum(path - mean_val)
  R <- max(Y) - min(Y)
  S <- sd(path)
  if (S <= 0 || R <= 0) return(NA_real_)
  log(R / S) / log(n)
}

estimate_whittle <- function(path,
                             H_grid = seq(0.1, 0.9, by = 0.02),
                             m_frac = 0.1) {
  dx <- diff(path)
  N <- length(dx)
  if (N < 64) return(NA_real_)
  dx <- dx - mean(dx)
  fft_vals <- fft(dx)
  periodogram <- (Mod(fft_vals)^2) / N
  max_j <- floor(N / 2)
  m_raw <- floor(N^0.6)
  m <- max(5, floor(m_frac * max_j), m_raw)
  m <- min(m, max_j)
  if (m < 5) return(NA_real_)
  j <- seq_len(m)
  lambda <- 2 * pi * j / N
  I_vals <- Re(periodogram[j + 1])
  scores <- sapply(H_grid, function(H) {
    shape <- lambda^(-(2 * H - 1))
    shape <- pmax(shape, 1e-8)
    sigma2_hat <- mean(I_vals / shape)
    sigma2_hat <- max(sigma2_hat, 1e-8)
    f_hat <- sigma2_hat * shape
    sum(log(f_hat) + I_vals / f_hat)
  })
  H_grid[which.min(scores)]
}

# --- PATCHED compute_segment_posteriors with logging ---
compute_segment_posteriors <- function(path, L, a = 0.5) {
  dx <- diff(path)
  n <- length(dx)
  message(sprintf("[post] L=%d, n_dx=%d", L, n))
  if (n < L * 2) {
    message(sprintf("[post] L=%d -> n_dx < 2L (%d < %d) -> NULL", L, n, 2 * L))
    return(NULL)
  }
  N_seg <- floor(n / L)
  if (N_seg < 2) {
    message(sprintf("[post] L=%d -> N_seg=%d < 2 -> NULL", L, N_seg))
    return(NULL)
  }
  message(sprintf("[post] L=%d -> N_seg=%d, L*N_seg=%d", L, N_seg, L * N_seg))
  dx <- dx[1:(L * N_seg)]
  segments <- split(dx, rep(seq_len(L), each = N_seg))
  out <- lapply(seq_along(segments), function(k) {
    seg <- segments[[k]]
    s <- sign(seg)
    s[s == 0] <- NA
    crossings <- sum(s[-1] * s[-length(s)] < 0, na.rm = TRUE)
    N_pairs <- max(1, length(seg) - 1)
    alpha_post <- crossings + 1 - a
    beta_post  <- (N_pairs - crossings) + 1 - a
    eps <- 1e-3
    alpha_post <- max(alpha_post, eps)
    beta_post  <- max(beta_post, eps)
    alpha_post <- min(alpha_post, 100)
    beta_post  <- min(beta_post, 100)
    if (k == 1) {
      message(sprintf(
        "[post] L=%d seg1: crossings=%d, N_pairs=%d, alpha=%.4f, beta=%.4f",
        L, crossings, N_pairs, alpha_post, beta_post
      ))
    }
    list(
      alpha = alpha_post,
      beta = beta_post,
      N_pairs = N_pairs
    )
  })
  out
}

segment_H_summary <- function(alpha, beta, n_draws = 2000, alpha_ci = 0.05) {
  p_draws <- rbeta(n_draws, alpha, beta)
  p_draws <- pmin(pmax(p_draws, 1e-6), 1 - 1e-6)
  H_draws <- 1 + log2(cos(pi * p_draws / 2))
  H_mean <- mean(H_draws)
  H_low <- quantile(H_draws, probs = alpha_ci / 2)
  H_high <- quantile(H_draws, probs = 1 - alpha_ci / 2)
  c(H_mean = H_mean, H_low = H_low, H_high = H_high)
}

# --- PATCHED compute_segment_H_trajectory ---
compute_segment_H_trajectory <- function(path, L, a = 0.5, n_draws = 2000, alpha_ci = 0.05) {
  dx <- diff(path)
  n <- length(dx)
  if (n < L * 2) return(NULL)
  N_seg <- floor(n / L)
  if (N_seg < 2) return(NULL)
  idx <- seq_len(L * N_seg)
  dx <- dx[idx]
  segments <- split(dx, rep(seq_len(L), each = N_seg))
  res <- data.frame(
    segment = integer(L),
    mid_idx = numeric(L),
    H_mean = numeric(L),
    H_low = numeric(L),
    H_high = numeric(L)
  )
  for (k in seq_len(L)) {
    seg <- segments[[k]]
    s <- sign(seg)
    s[s == 0] <- NA
    crossings <- sum(s[-1] * s[-length(s)] < 0, na.rm = TRUE)
    N_pairs <- max(1, length(seg) - 1)
    alpha_post <- crossings + 1 - a
    beta_post  <- (N_pairs - crossings) + 1 - a
    eps <- 1e-3
    alpha_post <- max(alpha_post, eps)
    beta_post  <- max(beta_post, eps)
    alpha_post <- min(alpha_post, 100)
    beta_post  <- min(beta_post, 100)
    stats <- segment_H_summary(alpha_post, beta_post, n_draws = n_draws, alpha_ci = alpha_ci)
    res$segment[k] <- k
    res$mid_idx[k] <- 1 + (k - 0.5) * N_seg
    res$H_mean[k] <- stats["H_mean"]
    res$H_low[k] <- stats["H_low"]
    res$H_high[k] <- stats["H_high"]
  }
  res
}

# ==== numerically stable f_L + robust normalization with logging ====
compute_f_L <- function(post_list,
                        grid_p = seq(1e-4, 1 - 1e-4, length.out = 600)) {
  if (length(post_list) == 0) {
    message("[fL] post_list empty -> NULL")
    return(NULL)
  }
  mat <- sapply(post_list, function(pars) {
    logd <- dbeta(grid_p, pars$alpha, pars$beta, log = TRUE)
    logd_shift <- logd - max(logd, na.rm = TRUE)
    d <- exp(logd_shift)
    d[!is.finite(d)] <- 0
    d
  })
  f_L <- rowMeans(mat)
  f_L[!is.finite(f_L)] <- 0
  f_min <- min(f_L, na.rm = TRUE)
  f_max <- max(f_L, na.rm = TRUE)
  f_sum <- sum(f_L, na.rm = TRUE)
  message(sprintf("[fL] range=[%.4e, %.4e], sum(f)=%.4e", f_min, f_max, f_sum))
  data.frame(p = grid_p, f = f_L)
}

# --- PATCHED UNIMODALITY TEST (robust to NAs, treat ambiguity as TRUE) ---
is_unimodal <- function(f) {
  if (length(f) < 5) return(TRUE)

  # Smooth and remove non-finite values
  fs <- stats::filter(f, rep(1/5, 5), sides = 2)
  fs <- as.numeric(fs)
  fs <- fs[is.finite(fs)]
  if (length(fs) < 5) return(TRUE)

  # Derivative and remove non-finite values
  d <- diff(fs)
  d <- d[is.finite(d)]
  if (length(d) < 3) return(TRUE)

  d[abs(d) < 1e-6] <- 0
  signs <- sign(d)
  signs <- signs[signs != 0]

  if (length(signs) < 3) return(TRUE)

  res <- all(diff(signs) <= 0)
  if (is.na(res)) TRUE else res
}

# --- PATCHED select_optimal_L with logging and robust unimodal_flags ---
select_optimal_L <- function(path,
                             candidate_Ls = c(2, 4, 8, 16),
                             a = 0.5,
                             grid_p = seq(1e-4, 1 - 1e-4, length.out = 600)) {
  dx <- diff(path)
  message(sprintf(
    "[select_L] path_len=%d, dx_len=%d, candidate_Ls=%s",
    length(path), length(dx), paste(candidate_Ls, collapse = ",")
  ))
  results <- list()
  for (L in sort(unique(candidate_Ls))) {
    message(sprintf("[select_L] Trying L=%d", L))
    post <- tryCatch(
      compute_segment_posteriors(path, L, a),
      error = function(e) {
        message(sprintf("[select_L] ERROR in compute_segment_posteriors(L=%d): %s", L, e$message))
        NULL
      }
    )
    if (is.null(post)) {
      message(sprintf("[select_L] L=%d -> post=NULL (skipping)", L))
      next
    }
    message(sprintf("[select_L] L=%d -> got %d segments", L, length(post)))
    fL_df <- tryCatch(
      compute_f_L(post, grid_p),
      error = function(e) {
        message(sprintf("[select_L] ERROR in compute_f_L(L=%d): %s", L, e$message))
        NULL
      }
    )
    if (is.null(fL_df)) {
      message(sprintf("[select_L] L=%d -> fL_df=NULL (skipping)", L))
      next
    }
    f_min <- min(fL_df$f, na.rm = TRUE)
    f_max <- max(fL_df$f, na.rm = TRUE)
    f_sum <- sum(fL_df$f, na.rm = TRUE)
    message(sprintf("[select_L] L=%d -> fL range=[%.4e, %.4e], sum(f)=%.4e", L, f_min, f_max, f_sum))
    uni <- is_unimodal(fL_df$f)
    message(sprintf("[select_L] L=%d -> unimodal=%s", L, uni))
    results[[as.character(L)]] <- list(
      L = L,
      post = post,
      fL = fL_df,
      unimodal = uni
    )
  }
  if (length(results) == 0) {
    message("[select_L] No valid L found -> returning NULL")
    return(NULL)
  }
  Ls <- as.numeric(names(results))
  unimodal_flags_raw <- sapply(results, function(entry) entry$unimodal)
  # Treat NA as TRUE (only reject when clearly multimodal)
  unimodal_flags <- ifelse(is.na(unimodal_flags_raw), TRUE, unimodal_flags_raw)
  message(sprintf(
    "[select_L] Finished: candidate Ls=%s, unimodal_flags=%s",
    paste(Ls, collapse = ","),
    paste(unimodal_flags, collapse = ",")
  ))
  eligible <- names(results)[unimodal_flags & Ls > 1]
  if (length(eligible) > 0) {
    chosen <- results[[eligible[1]]]
    message(sprintf("[select_L] Choosing smallest unimodal L>1: L_star=%s", eligible[1]))
  } else {
    chosen <- results[[1]]
    message(sprintf("[select_L] No unimodal L>1; falling back to first L=%d", chosen$L))
  }
  chosen$L_star <- chosen$L
  chosen
}

normalize_density <- function(fL_df) {
  dp <- diff(fL_df$p)[1]
  density <- fL_df$f
  density[!is.finite(density)] <- 0          # remove NaN/Inf
  density <- pmax(density, 0)
  total <- sum(density * dp)
  if (!is.finite(total) || total <= 0) {
    density <- rep(1 / nrow(fL_df), nrow(fL_df))
    total <- sum(density * dp)
  }
  density / total
}

# --- PATCHED credible_p_interval: NA-safe, robust, clamps/interpolates ---
credible_p_interval <- function(fL_df, alpha = 0.05) {
  density <- normalize_density(fL_df)
  dp <- diff(fL_df$p)[1]

  # Basic sanity checks
  if (!is.finite(dp) || dp <= 0) {
    return(c(p_min = NA_real_, p_max = NA_real_))
  }

  cdf_raw <- cumsum(density * dp)

  if (any(!is.finite(cdf_raw))) {
    return(c(p_min = NA_real_, p_max = NA_real_))
  }

  # Clamp CDF to [0,1]
  cdf_raw <- pmin(pmax(cdf_raw, 0), 1)

  # Enforce weakly increasing CDF
  eps <- 1e-10
  for (i in 2:length(cdf_raw)) {
    if (cdf_raw[i] < cdf_raw[i - 1]) {
      cdf_raw[i] <- cdf_raw[i - 1]  # or + eps for strict
    }
  }

  keep <- !duplicated(cdf_raw)
  cdf <- cdf_raw[keep]
  p   <- fL_df$p[keep]

  # Degenerate case: CDF is essentially flat (bad, fallback to mean!)
  if (length(cdf) < 2 || diff(range(cdf)) < 1e-8) {
    # Fall back to a point mass at the posterior mean of p
    p_mean <- sum(p * density[keep] * dp) / sum(density[keep] * dp)
    return(c(p_min = p_mean, p_max = p_mean))
  }

  # Safe to interpolate for quantiles
  p_min <- approx(cdf, p, xout = alpha / 2,      rule = 2)$y
  p_max <- approx(cdf, p, xout = 1 - alpha / 2,  rule = 2)$y

  c(p_min = as.numeric(p_min), p_max = as.numeric(p_max))
}

# --- PATCHED map_p_to_H_interval: NA-safe, clamps boundaries, robust ---
map_p_to_H_interval <- function(p_min, p_max) {
  if (!is.finite(p_min) || !is.finite(p_max)) {
    return(c(H_min = NA_real_, H_max = NA_real_))
  }
  # Clamp p away from 0/1 (where cos(pi p/2) = 0) to avoid log(-)
  eps <- 1e-6
  p_min <- min(max(p_min, eps), 1 - eps)
  p_max <- min(max(p_max, eps), 1 - eps)

  H_min <- 1 + log2(cos(pi * p_max / 2))
  H_max <- 1 + log2(cos(pi * p_min / 2))

  # If something still explodes, mark as NA
  if (!is.finite(H_min) || !is.finite(H_max)) {
    H_min <- NA_real_
    H_max <- NA_real_
  }

  c(H_min = H_min, H_max = H_max)
}

EH_and_varH <- function(fL_df) {
  density <- normalize_density(fL_df)
  dp <- diff(fL_df$p)[1]
  g <- 1 + log2(cos(pi * fL_df$p / 2))
  g[!is.finite(g)] <- 0
  density[!is.finite(density)] <- 0
  EH  <- sum(g * density * dp)
  EH2 <- sum(g^2 * density * dp)
  if (!is.finite(EH))  EH  <- NA_real_
  if (!is.finite(EH2)) EH2 <- NA_real_
  varH <- max(EH2 - EH^2, 0, na.rm = TRUE)
  c(EH = EH, varH = varH)
}

# --- PATCHED compute_segmentation_summary: NA-robust, fallback if CI fails ---
compute_segmentation_summary <- function(path,
                                         candidate_Ls = c(2, 4, 8, 16),
                                         a = 0.5,
                                         alpha_ci = 0.05,
                                         grid_p = seq(1e-4, 1 - 1e-4, length.out = 600)) {
  dx <- diff(path)
  message(sprintf("[SegSummary] path_len=%d, dx_len=%d", length(path), length(dx)))
  if (length(dx) < 4) {
    message("[SegSummary] dx too short (<4) -> returning NULL")
    return(NULL)
  }
  optimal <- select_optimal_L(path, candidate_Ls = candidate_Ls, a = a, grid_p = grid_p)
  if (is.null(optimal)) {
    message("[SegSummary] select_optimal_L returned NULL")
    return(NULL)
  }
  message(sprintf("[SegSummary] Chosen L_star=%d", optimal$L_star))
  H_stats <- EH_and_varH(optimal$fL)   # returns c(EH, varH)
  H_mean  <- H_stats["EH"]
  # If we can't even get a mean, abort this frame
  if (!is.finite(H_mean)) {
    message("[SegSummary] EH is not finite -> returning NULL for this frame")
    return(NULL)
  }
  credible   <- credible_p_interval(optimal$fL, alpha = alpha_ci)
  H_interval <- map_p_to_H_interval(credible["p_min"], credible["p_max"])
  # If CI failed, use a degenerate interval at the mean
  if (!is.finite(H_interval["H_min"]) || !is.finite(H_interval["H_max"])) {
    H_interval["H_min"] <- H_mean
    H_interval["H_max"] <- H_mean
  }
  message(sprintf(
    "[SegSummary] Global H: mean=%.4f, low=%.4f, high=%.4f",
    H_mean, H_interval["H_min"], H_interval["H_max"]
  ))
  segments <- compute_segment_H_trajectory(
    path,
    optimal$L_star,
    a = a,
    n_draws = 1200,
    alpha_ci = alpha_ci
  )
  list(
    L_star = optimal$L_star,
    fL = optimal$fL,
    global = c(
      H_mean = H_mean,
      H_low  = H_interval["H_min"],
      H_high = H_interval["H_max"]
    ),
    segments = segments
  )
}

compute_estimator_trajectory <- function(path, steps) {
  steps <- sort(unique(steps))
  df <- data.frame(
    step = steps,
    zero = NA_real_,
    quad = NA_real_,
    rs = NA_real_,
    whittle = NA_real_
  )
  for (i in seq_along(steps)) {
    sample_path <- path[1:steps[i]]
    df$zero[i] <- estimate_zero_crossings(sample_path)
    df$quad[i] <- estimate_quadratic_variation(sample_path)
    df$rs[i] <- estimate_rs(sample_path)
    df$whittle[i] <- estimate_whittle(sample_path)
  }
  df
}

# --------------------------------------------------------------------
# Improved create_estimator_animation: Bayesian line and CI always visible
# (patched: robustly recompute H_mean/H_low/H_high from fL)
# --------------------------------------------------------------------
create_estimator_animation <- function(est_df,
                                      H_true,
                                      path,
                                      frame_indices,
                                      n_steps = max(est_df$step),
                                      candidate_Ls = c(2, 4, 8, 16)) {
  frames <- list()
  method_colors <- c(
    zero    = "#1f78b4",
    quad    = "#33a02c",
    rs      = "#e31a1c",
    whittle = "#ff7f00",
    bayes   = "#6a3d9a"
  )
  method_labels <- c(
    zero    = "Zero-crossings",
    quad    = "Quadratic variation",
    rs      = "Rescaled Range (R/S)",
    whittle = "Whittle",
    bayes   = "Bayesian segmentation"
  )
  data_methods <- c("zero", "quad", "rs", "whittle")
  steps <- est_df$step
  n_frames <- length(steps)
  bayes_mean <- rep(NA_real_, n_frames)
  bayes_low  <- rep(NA_real_, n_frames)
  bayes_high <- rep(NA_real_, n_frames)
  for (i in seq_len(n_frames)) {
    step <- steps[i]
    if (step < 50) {
      message(sprintf("[Bayes] Step %d ignored, path too short for segmentation summary", step))
      next
    }

    seg_summary <- compute_segmentation_summary(
      path[1:step],
      candidate_Ls = candidate_Ls
    )

    if (is.null(seg_summary) || is.null(seg_summary$fL)) {
      message(sprintf("[Bayes] No usable segmentation summary at frame %d (step=%d)", i, step))
      next
    }

    # Recompute global H from the returned fL to avoid any issues with seg_summary$global
    H_stats   <- EH_and_varH(seg_summary$fL)   # c(EH, varH)
    H_mean    <- as.numeric(H_stats["EH"])

    if (!is.finite(H_mean)) {
      message(sprintf("[Bayes] Recomputed EH not finite at frame %d (step=%d)", i, step))
      next
    }

    cred_p    <- credible_p_interval(seg_summary$fL, alpha = 0.05)
    H_int     <- map_p_to_H_interval(cred_p["p_min"], cred_p["p_max"])

    H_low  <- as.numeric(H_int["H_min"])
    H_high <- as.numeric(H_int["H_max"])

    # If CI failed, collapse to a point at the mean
    if (!is.finite(H_low) || !is.finite(H_high)) {
      H_low  <- H_mean
      H_high <- H_mean
    }

    message(sprintf(
      "[Bayes] Global (recomputed): H_mean=%.4f, H_low=%.4f, H_high=%.4f at frame %d (step=%d)",
      H_mean, H_low, H_high, i, step
    ))

    bayes_mean[i] <- H_mean
    bayes_low[i]  <- H_low
    bayes_high[i] <- H_high
  }
  message("[Bayes] Summary stats over all frames:")
  message(sprintf("  > Number of frames: %d", n_frames))
  message(sprintf("  > Non-NA Bayes means: %d", sum(!is.na(bayes_mean))))
  message(sprintf("  > Bayes means (first 10, na.rm=TRUE): %s", 
                  paste(formatC(na.omit(bayes_mean[1:min(length(bayes_mean),10)]), digits=4), collapse=", ")))
  combined_vals <- c(
    unlist(est_df[, data_methods], use.names = FALSE),
    bayes_mean, bayes_low, bayes_high,
    H_true
  )
  combined_vals <- combined_vals[is.finite(combined_vals)]
  if (length(combined_vals) == 0) {
    ylim <- c(0.1, 0.9)
    message("[Bayes] Y-limits defaulted to (0.1, 0.9) because no valid data")
  } else {
    y_min  <- min(combined_vals, na.rm = TRUE)
    y_max  <- max(combined_vals, na.rm = TRUE)
    margin <- max(0.05, 0.15 * (y_max - y_min))
    ylim   <- c(max(-1, y_min - margin), min(1.5, y_max + margin))
    message(sprintf("[Bayes] Y-limits set to: c(%.4f, %.4f)", ylim[1], ylim[2]))
  }
  for (i in seq_len(n_frames)) {
    step    <- est_df$step[i]
    current <- est_df[1:i, ]
    temp_file <- tempfile(fileext = ".png")
    png(temp_file, width = 700, height = 500, res = 100)
    par(mar = c(4, 4, 3, 1))
    plot(
      current$step,
      current$zero,
      type = "n",
      xlim = c(1, n_steps),
      ylim = ylim,
      xlab = "Sample size",
      ylab = "Estimated H",
      main = paste0("Estimators approaching H = ", round(H_true, 2)),
      sub  = paste0("Step: ", step, " / ", n_steps),
      cex.main = 1.4,
      cex.lab  = 1.2
    )
    grid(nx = 10, ny = 10, col = "lightgray", lty = 3)
    abline(h = H_true, col = "#4d4d4d", lty = 2, lwd = 1.5)
    for (method in data_methods) {
      values <- current[[method]]
      valid  <- !is.na(values)
      if (any(valid)) {
        lines(
          current$step[valid],
          values[valid],
          col = method_colors[[method]],
          lwd = 2
        )
        last_idx <- tail(which(valid), 1)
        points(
          current$step[last_idx],
          values[last_idx],
          col = method_colors[[method]],
          pch = 16,
          cex = 1.2
        )
      }
    }
    valid_bayes <- !is.na(bayes_mean[1:i])
    message(sprintf("[Bayes-Plot] Frame %d/%d: valid_bayes sum=%d", i, n_frames, sum(valid_bayes)))
    if (sum(valid_bayes) > 0) {
      message(sprintf("[Bayes-Plot] Drawing line for steps: %s", paste(steps[valid_bayes], collapse=", ")))
      message(sprintf("[Bayes-Plot] Drawing mean values: %s", paste(formatC(bayes_mean[valid_bayes], digits=4), collapse=", ")))
      lines(
        steps[valid_bayes],
        bayes_mean[valid_bayes],
        col = method_colors[["bayes"]],
        lwd = 2,
        lty = 2
      )
      last_idx <- tail(which(valid_bayes), 1)
      message(sprintf("[Bayes-Plot] Drawing last bayes point at step %d, mean %.4f, low=%.4f, high=%.4f",
                      steps[last_idx], bayes_mean[last_idx], bayes_low[last_idx], bayes_high[last_idx]))
      points(
        steps[last_idx],
        bayes_mean[last_idx],
        col = method_colors[["bayes"]],
        pch = 17,
        cex = 1.2
      )
      if (!is.na(bayes_low[last_idx]) && !is.na(bayes_high[last_idx])) {
        arrows(
          x0 = steps[last_idx],
          y0 = bayes_low[last_idx],
          x1 = steps[last_idx],
          y1 = bayes_high[last_idx],
          code = 3,
          angle = 90,
          length = 0.05,
          col = method_colors[["bayes"]],
          lwd = 1.1
        )
      } else {
        message(sprintf("[Bayes-Plot] CI missing for last_idx=%d: bayes_low=%.4f, bayes_high=%.4f",
                        last_idx, bayes_low[last_idx], bayes_high[last_idx]))
      }
    } else {
      message(sprintf("[Bayes-Plot] No bayesian estimate available to plot for frames 1:%d", i))
    }
    legend(
      "topright",
      legend = method_labels,
      col    = method_colors,
      lwd    = 2,
      lty    = c(1, 1, 1, 1, 2),
      pch    = c(16, 16, 16, 16, 17),
      bty    = "n",
      cex    = 0.8
    )
    usr      <- par("usr")
    label_y  <- usr[4] - 0.05 * diff(usr[3:4])
    y_step   <- 0.05 * diff(usr[3:4])
    label_x  <- usr[1] + 0.02 * diff(usr[1:2])
    idx_lab  <- 0
    for (method in data_methods) {
      last_val <- tail(na.omit(current[[method]]), 1)
      if (length(last_val) == 0) next
      text(
        x = label_x,
        y = label_y - idx_lab * y_step,
        labels = paste0(
          method_labels[[method]], ": ",
          formatC(last_val, digits = 2, format = "f")
        ),
        col = method_colors[[method]],
        adj = c(0, 1),
        cex = 0.85
      )
      idx_lab <- idx_lab + 1
    }
    dev.off()
    frames[[length(frames) + 1]] <- image_read(temp_file)
    unlink(temp_file)
  }
  animation <- do.call(c, frames)
  image_animate(animation, fps = 10, loop = 1)
}
```
```{r}
#| context: server

anim_state <- reactiveValues(
  animation = NULL,
  H = 0.5,
  n_steps = 500,
  method = "cholesky"
)
est_state <- reactiveValues(
  animation = NULL
)

observeEvent(input$resample, {
  H <- input$hurst
  n <- input$n_steps
  method <- input$method
  
  frame_indices <- calc_frame_indices(n)

  path <- generate_fbm(n, H, method)
  anim_state$animation <- create_animation_frames(path, H, n, method, frame_indices)
  anim_state$H <- H
  anim_state$n_steps <- n
  anim_state$method <- method

  est_state$animation <- NULL
  estimator_df <- compute_estimator_trajectory(path, frame_indices)
  est_state$animation <- create_estimator_animation(
    estimator_df,
    H,
    path,
    frame_indices,
    n_steps = n
  )
})

output$simulation_plot <- renderImage({
  if (is.null(anim_state$animation)) {
    temp_file <- tempfile(fileext = ".png")
    png(temp_file, width = 700, height = 500)
    plot(0, type = "n", axes = FALSE, xlab = "", ylab = "")
    text(0.5, 0.5, "wait", 
         cex = 1.5, col = "gray60")
    dev.off()
    
    list(src = temp_file, contentType = "image/png", width = "100%", height = "450px")
  } else {
    temp_file <- tempfile(fileext = ".gif")
    image_write(anim_state$animation, path = temp_file)
    
    list(src = temp_file, contentType = "image/gif", width = "100%", height = "450px", deleteFile = TRUE)
  }
}, deleteFile = FALSE)

output$estimator_plot <- renderImage({
  if (is.null(est_state$animation)) {
    temp_file <- tempfile(fileext = ".png")
    png(temp_file, width = 700, height = 500)
    plot(0, type = "n", axes = FALSE, xlab = "", ylab = "")
    text(0.5, 0.5, "wait", 
         cex = 1.3, col = "gray50")
    dev.off()
    
    list(src = temp_file, contentType = "image/png", width = "100%", height = "450px")
  } else {
    temp_file <- tempfile(fileext = ".gif")
    image_write(est_state$animation, path = temp_file)
    
    list(src = temp_file, contentType = "image/gif", width = "100%", height = "450px", deleteFile = TRUE)
  }
}, deleteFile = FALSE)
```
::: {style="display: flex; gap: 20px; align-items: flex-start;"}

::: {style="flex: 0 0 25%; background-color: #f0f0f0; padding: 15px; border-radius: 5px;"}

```{r}
# Add CSS styling for compact controls
tags$style(HTML("
  .compact-controls .form-group {
    margin-bottom: 12px;
  }
  .compact-controls .form-group label {
    font-size: 13px;
    margin-bottom: 4px;
  }
  .compact-controls select {
    font-size: 12px;
    padding: 4px 6px;
  }
  .compact-controls input[type='slider'] {
    font-size: 12px;
  }
  .compact-controls .shiny-input-container {
    font-size: 12px;
  }
"))

tags$div(class = "compact-controls",
  selectInput(
    "method",
    strong("Simulation Method:"),
    choices = list(
      "Cholesky (Exact, O(N³))" = "cholesky",
      "Hosking (Exact, O(N²))" = "hosking",
      "FFT (Near-exact, O(N log N))" = "fft",
      "Spectral (Approx, O(N log N))" = "spectral",
      "Corr. Random Walk (Approx, fast)" = "crw",
      "Random Midpoint Displacement (Exact*)" = "rmd"
    ),
    selected = "cholesky"
  ),
  
sliderInput(
  "hurst",
  strong("Hurst Exponent (H):"),
  min = 0.1,
  max = 0.9,
  value = 0.5,
  step = 0.05
  ),

numericInput(
  "n_steps",
  strong("Time Steps:"),
  value = 500,
  min = 100,
  max = 2000,
  step = 100
  ),

actionButton("resample", "Generate Sample", class = "btn-primary btn-block", width = "100%")
)
```

:::

::: {style="flex: 1; min-width: 0;"}

```{r}
plotOutput("simulation_plot", height = "320px")
```


```{r}
imageOutput("estimator_plot", height = "320px")
```
</div>

:::

:::

---
